---
title: "Coding_Exercises"
author: "Neda Safari"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("setup.R")
```


1.Create a new column in the bison dataset that calculates the individual’s age at the time of observation.
```{r}
knz_bison%>%
  head(5)
bison2<- knz_bison%>%
  mutate(indiv_age= rec_year- animal_yob)
bison2%>%
  head(5)
```


2.Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
bisonWeight<- function(knz_bison, x) {
  knz_bison%>%
    filter(animal_weight>= x)
}
```

3.Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.
```{r}
bison_test<-bison2%>%
  drop_na()

bison_test%>%
  ggplot(aes(animal_sex, animal_weight))+
  geom_boxplot()

t.test(animal_weight ~ animal_sex, data= bison_test)
```






















